On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-09-17 MS.tex
Change in Fig code

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item A plant's growth rate (GR) has often been seen as a central element of it's ecological strategy, and as ultimately linked to its traits. Yet, the literature is inconsistent about the empirical correlation between functional traits and GR, casting doubt on the capacity of traits to predict growth.

@@

Light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size. For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes. Similarly, instead of a negative correlation between WD and growth across all plant stages, \citep{Iida:2014ep,Iida:2014hq} found a negative correlation at small size that disappeared when trees were larger. \citet{Iida:2014hq} explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits. Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh. This points to one of the possible limitations in our meta-analysis, where trees with diameter above 10 cm were pooled as ``adult''.

>>>>

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary 274/350}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item A plant's growth rate (GR) has often been seen as a central element of it's ecological strategy, and as ultimately linked to its traits. Yet, the literature is inconsistent about the empirical correlation between functional traits and GR, casting doubt on the capacity of traits to predict growth.

@@

Light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size. For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes. Similarly, instead of a negative correlation between WD and growth across all plant stages,  some studies found a negative correlation at small size that disappeared when trees were larger \citep{Iida:2014ep,Iida:2014hq}. The authors explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits. Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh. This points to one of the possible limitations in our meta-analysis, where trees with diameter above 10 cm were pooled as ``adult''.
